---
title: "Titanic random KMEANs, KNN"
author: "Bhasheyam"
date: "19 December 2017"
output: html_document
---

```{r}
Tittrain = read.csv("train.csv")
Tittest = read.csv("test.csv")
Tittest$Survived = ""
```

```{r}
fix(Tittrain)
```
```{r}
names(Tittest)
```


```{r}
Tittrain$Sex = as.factor(Tittrain$Sex)
Tittrain$Embarked = as.factor(Tittrain$Embarked)
```

```{r}
Tittest$Sex = as.factor(Tittest$Sex)
Tittest$Embarked = as.factor(Tittest$Embarked)
```

```{r}
ageavg = mean(Tittrain$Age,na.rm=TRUE)
ageavg1 = mean(Tittest$Age,na.rm=TRUE)
ageavg
```

```{r}

change = function(x){
  if(is.na(x[6])){
    x[6] = ageavg
  }
  else{
    x[6] = x[6]
  }
}

change1 = function(x){
  if(is.na(x[5])){
    x[5] = ageavg
  }
  else{
    x[5] = x[5]
  }
}
Tittrain$Age = apply(Tittrain, 1, change)
Tittest$Age = apply(Tittest, 1, change1)
```


```{r}
fix(Tittrain)
```



```{r}
Tittrain$Age = as.numeric(Tittrain$Age)
Tittest$Age = as.numeric(Tittest$Age)
```

```{r}
Tittrain = subset(Tittrain, select = c( "Survived"  ,  "Pclass",  "Sex",  "Age", "SibSp",  "Parch",      
 "Embarked"   ))
```

```{r}
Tittest = subset(Tittest, select = c( "Survived"  ,  "Pclass",  "Sex",  "Age", "SibSp",  "Parch", "Embarked"   ))
```



```{r}
Tittrain$Survived = as.numeric(Tittrain$Survived)
Tittrain$Survived = as.factor(Tittrain$Survived)
```
```{r}
for(i in 1:ncol(Tittrain)){
  Tittrain[is.na(Tittrain[,i]), i] <- mean(Tittrain[,i], na.rm = TRUE)
}
```
```{r}
fix(Tittrain)
```

```{r}
for(i in 1:ncol(Tittest)){
  Tittest[is.na(Tittest[,i]), i] <- mean(Tittest[,i], na.rm = TRUE)
}
```


```{r}
library(mlr)
Ttask = makeClassifTask(data = Tittrain,target = "Survived" )
Tetask = makeClassifTask(data = Tittest,target = "Survived")
```

```{r}
set.seed(1)
svmt = makeLearner("classif.ksvm", predict.type = "response")

randomcross = makeResampleDesc("CV",iters = 2L)

svmparameter<- makeParamSet(makeNumericParam("C", lower = -5, upper = 5, trafo = function(x) 2^x))


svmcontrol = makeTuneControlGrid()
svmtunel = tuneParams(svmt, task = Ttask, resampling = randomcross, par.set  = svmparameter, control = svmcontrol, measures = acc)
```
```{r}
svmtunel$x
```


```{r}
svmtunel$y
```
```{r}
svmmodell = setHyperPars(svmt,par.vals = svmtunel$x)
svmtrainl = train(svmmodell, Ttask)
getLearnerModel(svmtrainl)

```

```{r}
predictsvml = predict(svmtrainl, Tetask)
```
```{r}
datacsv31 = as.data.frame(temptest$PassengerId)  
datacsv31$Survived = logpridect$data$response
```
```{r}
write.csv(datacsv31, file = "Submisionl.csv", row.names = FALSE)
```
```

```{r}
set.seed(1)
svmlearner = makeLearner("classif.ksvm", predict.type = "response")

randomcross = makeResampleDesc("CV",iters = 3L)

svmparameter<- makeParamSet(makeNumericParam("C", lower = -5, upper = 5, trafo = function(x) 2^x),
                            makeDiscreteParam("sigma", values = 2^c(-8,-4,0,4))) #RBF Kernel Parameter

svmcontrol = makeTuneControlGrid()
svmtune= tuneParams("classif.ksvm", task = traintask, resampling = randomcross, par.set  = svmparameter, control = svmcontrol, measures = acc)
```



```{r}
svmtune$y
```



```{r}
svmtune$x

```




```{r}
svmmodel = setHyperPars(svmlearner,par.vals = svmtune$x)
svmtrain = train(svmmodel, traintask)
getLearnerModel(svmtrain)
```


```{r}
predictsvm = predict(svmtrain, testtask)
table (Autotest$high_mileage, predictsvm$data$response)
```


```{r}
library(class)

Train1 = Train[3:14]
Test1 = Test[3:14]
model=knn(train=Train1,test = Test1, cl=Train$countclass,k=10)
summary(model)
table(Test$countclass,model)
```






