---
title: "Clasifer battle with Auto dataset"
author: "Bhasheyam Krishnan "
date: "14 November 2017"
output: pdf_document
---
1. Create a new column in the dataset, high_mileage that is true if mpg > mean(mpg). Else it’s
false. You will try to predict these variables as a function of the predictors. DO NOT USE name
and origin is a categorical as before.

```{r}
Autodata = Auto[1:7]
Autodata$origin = as.factor(Auto$origin)
Autodata$high_mileage = apply(Autodata, 1, function(x) x[1] > mean(Autodata$mpg))
Autodata
```



-----------------------------------------------------------------------------------------------------------------
2. Set the seed to one and set up the data for 3-fold cross validation.
```{r}
set.seed(1)
jumble = runif(nrow(Autodata))
Autodata = Autodata[ordered(jumble),]
index = sample(2, nrow(Autodata), replace = TRUE, prob = c(0.80,0.20))
Autotrain = Autodata[index == 1,]
Autotest = Autodata[index == 2,]


```



-----------------------------------------------------------------------------------------------------------------
3. Guess which classifier will do best.

Answer :



-----------------------------------------------------------------------------------------------------------------
4. Predict high mpg with these classifiers:

```{r}
library(mlr)
traintask = makeClassifTask(data = Autotrain,target = "high_mileage")
testtask = makeClassifTask(data = Autotest, target = "high_mileage")
traintask

```
```{r}
traintask = normalizeFeatures(traintask,method = "standardize")
testtask = normalizeFeatures(testtask, method = "standardize")
traintask <- dropFeatures(task = traintask,features = c("mpg"))
testtask <- dropFeatures(task = testtask,features = c("mpg"))

```





a. Logistic regression tuning (i.e., with ridge regularization)
```{r}
logistic = makeLearner("classif.logreg",predict.type = "response")
cv.logistic = crossval(learner = logistic, task = traintask,iter = 3, stratify = TRUE,measures = acc,show.info = F)
cv.logistic$aggr
cv.logistic$measures.test
```
```{r}
logmodel = train(logistic,traintask)
getLearnerModel(logmodel)
```
```{r}
logpridect = predict(logmodel,testtask)

table(Autotest$high_mileage,logpridect$data$response)
```
Here the Acuuracy is 93 %



-----------------------------------------------------------------------------------------------------------------

b. Decision trees with tuning (e.g., you will set the splitting criterion)

```{r}
 tree <- makeLearner("classif.rpart", predict.type = "response")
```

```{r}
set_cv = makeResampleDesc("CV",iters = 3L)

```


```{r}
gs <- makeParamSet(makeIntegerParam("minsplit",lower = 10, upper = 50),
makeIntegerParam("minbucket", lower = 5, upper = 50),
makeNumericParam("cp", lower = 0.001, upper = 0.2))
```

```{r}
gscontrol =  makeTuneControlGrid()
```
```{r}
tune = tuneParams(learner = tree, resampling = set_cv, task = traintask, par.set = gs, control = gscontrol, measures = acc)
```



```{r}
tune$x
```
The above are the best tuning varaible from the tuning
```{r}
tune$y

```
```{r}
traintree = setHyperPars(tree,par.vals = tune$x)
```

Fitting the Tuning variable in the Tree

```{r}
destree = train(traintree,traintask)
getLearnerModel(destree)
```
```{r}
prp(destree$learner.model)
```


```{r}
library(rattle)	
fancyRpartPlot(destree$learner.model)	
```


```{r}
despredict = predict(destree,testtask)
table(Autotest$high_mileage,despredict$data$response)
```

Here the Accuracy is 91%



-----------------------------------------------------------------------------------------------------------------
c. Bagging with tuning


```{r}

baglearn = makeLearner("classif.boosting", predict.type = "response")

```
```{r}

```



-----------------------------------------------------------------------------------------------------------------
d. Random forest with tuning


```{r}
randomforest = makeLearner("classif.randomForest",predict.type = "response", par.vals = list(ntree = 200, mtry = 3))
randomforest$par.vals = list(importance = TRUE)

```


Creating a learner
```{r}
randomparam <- makeParamSet(
makeIntegerParam("ntree",lower = 50, upper = 500),
makeIntegerParam("mtry", lower = 3, upper = 10),
makeIntegerParam("nodesize", lower = 10, upper = 50)
)
randomcontrol <- makeTuneControlRandom(maxit = 50L)
randomcross = makeResampleDesc("CV",iter =  3L)
```


Finding the Tuning value

```{r}
randomtune <- tuneParams(learner = randomforest, resampling = randomcross, task = traintask, par.set = randomparam, control = randomcontrol, measures = acc)

```



```{r}
randomtune$y
```
```{r}
randomtune$x
```
The above are the best Tuning variable

```{r}
randomtree = setHyperPars(randomforest, par.vals = randomtune$x)
randomtrain = train(randomtree, traintask)
getLearnerModel(randomtrain)

```


```{r}
randompredict = predict(randomtrain,testtask)
table(Autotest$high_mileage, randompredict$data$response)
```
here the accuraccy is 94%
-----------------------------------------------------------------------------------------------------------------
e. Boosting with tuning




-----------------------------------------------------------------------------------------------------------------
f. SVM with linear kernel tuning

creating an learner , hyperparameter and Grid controller
```{r}
svmlearner = makeLearner("classif.ksvm", predict.type = "response")

svmparameter<- makeParamSet(
makeDiscreteParam("C", values = 2^c(-8,-4,-2,0)), #cost parameters
makeDiscreteParam("sigma", values = 2^c(-8,-4,0,4)) #RBF Kernel Parameter
)
svmcontrol = makeTuneControlGrid()
svmtune = tuneParams(svmlearner, task = traintask, resampling = randomcross, par.set  = svmparameter, control = svmcontrol, measures = acc)
```


```{r}
svmtune$y
```



```{r}
svmtune$x

```




```{r}
svmmodel = setHyperPars(svmlearner, par.vals  = svmtune$x)
svmtrain = train(svmmodel, traintask)
getLearnerModel(svmtrain)
```


```{r}
predictsvm = predict(svmtrain, testtask)
table (Autotest$high_mileage, predictsvm$data$response)
```
Same here the accuracy is also 94%

-----------------------------------------------------------------------------------------------------------------
g. SVM with polynomial kernel and tuning



-----------------------------------------------------------------------------------------------------------------

h. LDA analysis(bonus 5):
```{r}
ldalearner = makeLearner("classif.lda", predict.type = "response")
ldatrain = train(ldalearner, traintask)
predictlda = predict(ldatrain, testtask)
table(Autotest$high_mileage, predictlda$data$response)
```
Here the LDA accuracy is 91 %


```{r}
cvlda = crossval(ldalearner, task = traintask, ,iters = 3,stratify = TRUE,measures = acc,show.info = F)
cvlda$aggr
```





-----------------------------------------------------------------------------------------------------------------

5. Report
a. Report the accuracy if you predicted the most frequent class for all observations. This is
your baseline.






-----------------------------------------------------------------------------------------------------------------
b. Plot of cross validation accuracy as a function of the tuning parameter for each classifier.




-----------------------------------------------------------------------------------------------------------------

i. For the decision tree, plot the tree.




-----------------------------------------------------------------------------------------------------------------



c. Which classifier does best?




-----------------------------------------------------------------------------------------------------------------
d. Which one would you use? And does this classifier match your initial guess?












-----------------------------------------------------------------------------------------------------------------
