---
title: "Hw-7"
author: "Bhasheyam Krishnan - A23080078, Hemath Balakrishna - A20385274"
date: "14 November 2017"
output:
  word_document: default
  pdf_document: default
---
1. Create a new column in the dataset, high_mileage that is true if mpg > mean(mpg). Else it’s
false. You will try to predict these variables as a function of the predictors. DO NOT USE name
and origin is a categorical as before.

```{r}
library(ISLR)

Autodata = Auto[1:7]
Autodata$origin = as.factor(Auto$origin)
Autodata$high_mileage = apply(Autodata, 1, function(x) x[1] > mean(Autodata$mpg))
Autodata
summary(Autodata$high_mileage)
```



-----------------------------------------------------------------------------------------------------------------
2. Set the seed to one and set up the data for 3-fold cross validation.
```{r}
set.seed(1)
jumble = runif(nrow(Autodata))
Autodata = Autodata[ordered(jumble),]
index = sample(2, nrow(Autodata), replace = TRUE, prob = c(0.80,0.20))
Autotrain = Autodata[index == 1,]
Autotest = Autodata[index == 2,]
```



-----------------------------------------------------------------------------------------------------------------
3. Guess which classifier will do best.

Answer :

Random Forest, as it reduces overfitting: by averaging several trees, there is a significantly lower risk of overfitting than decision tree.

-----------------------------------------------------------------------------------------------------------------
4. Predict high mpg with these classifiers:

```{r}
library(mlr)
traintask = makeClassifTask(data = Autotrain,target = "high_mileage")
testtask = makeClassifTask(data = Autotest, target = "high_mileage")
traintask

```
```{r}
traintask = normalizeFeatures(traintask,method = "standardize")
testtask = normalizeFeatures(testtask, method = "standardize")
traintask <- dropFeatures(task = traintask,features = c("mpg"))
testtask <- dropFeatures(task = testtask,features = c("mpg"))

```





a. Logistic regression tuning (i.e., with ridge regularization)
```{r}
set.seed(1)
logistic = makeLearner("classif.logreg",predict.type = "response")
cv.logistic = crossval(learner = logistic, task = traintask,iter = 3, stratify = TRUE,measures = acc,show.info = F)
cv.logistic$aggr
cv.logistic$measures.test
```





```{r}
logmodel = train(logistic,traintask)
getLearnerModel(logmodel)
logmodel$task.desc$positive
```
```{r}
logpridect = predict(logmodel,testtask)

table(Autotest$high_mileage,logpridect$data$response)
```
Here the Acuuracy is 93 %




-----------------------------------------------------------------------------------------------------------------

b. Decision trees with tuning (e.g., you will set the splitting criterion)

```{r}
set.seed(1)
 tree <- makeLearner("classif.rpart", predict.type = "response")
```

```{r}
set_cv = makeResampleDesc("CV",iters = 10L)

```


```{r}
gs <- makeParamSet(makeIntegerParam("minsplit",lower = 10, upper = 50),
makeIntegerParam("minbucket", lower = 5, upper = 50),
makeNumericParam("cp", lower = 0.001, upper = 0.2))
```

```{r}
gscontrol =  makeTuneControlGrid()
```
```{r}
tune = tuneParams(learner = tree, resampling = set_cv, task = traintask, par.set = gs, control = gscontrol, measures = acc)
```



```{r}
tune$x
```
The above are the best tuning varaible from the tuning
```{r}
tune$y

```
```{r}
traintree = setHyperPars(tree,par.vals = tune$x)
```

Fitting the Tuning variable in the Tree

```{r}
destree = train(traintree,traintask)
getLearnerModel(destree)
```
```{r}
library(rpart.plot)
prp(destree$learner.model)
```


```{r}
library(rattle)	
fancyRpartPlot(destree$learner.model)	
```


```{r}
despredict = predict(destree,testtask)
table(Autotest$high_mileage,despredict$data$response)
```

Here the Accuracy is 92%



-----------------------------------------------------------------------------------------------------------------
c. Bagging with tuning


```{r}
set.seed(1)
baglearn = makeLearner("classif.rpart")
bag = makeBaggingWrapper(baglearn, bw.iters = 50, bw.replace = TRUE, bw.size = 0.8, bw.feats = 3/4)
cvbag = makeResampleDesc("CV", iters = 3)
r = resample(learner = bag, task = traintask, resampling = cvbag, show.info = FALSE)
r$aggr
```
```{r}
bagparam = makeParamSet( makeNumericParam("xval", lower = 1, upper = 15))
badcontrol = makeTuneControlGrid()
bagtune = tuneParams(learner = bag, task = traintask, resampling =set_cv,par.set = bagparam,control = badcontrol, measures = acc )
```


```{r}
bagtune$y
```
```{r}
bagtune$x
```
```{r}
bagging =  setHyperPars(bag, par.vals = bagtune$x)
```




```{r}
bagtrain = train(bag,traintask)
bagtrain$learner.model$next.model
```
```{r}
predictbag = predict(bagtrain, testtask)
table(Autotest$high_mileage,predictbag$data$response)

```

Here the Accuracy is 94 %

-----------------------------------------------------------------------------------------------------------------
d. Random forest with tuning


```{r}

randomforest = makeLearner("classif.randomForest",predict.type = "response", par.vals = list(ntree = 200, mtry = 3))
randomforest$par.vals = list(importance = TRUE)

```


Creating a learner
```{r}
set.seed(1)
randomparam <- makeParamSet(
makeIntegerParam("ntree",lower = 50, upper = 500),
makeIntegerParam("mtry", lower = 3, upper = 10),
makeIntegerParam("nodesize", lower = 10, upper = 50)
)
randomcontrol = makeTuneControlRandom(maxit = 50L)
randomcross = makeResampleDesc("CV",iter =  3L)
```


Finding the Tuning value

```{r}
randomtune <- tuneParams(learner = randomforest, resampling = randomcross, task = traintask, par.set = randomparam, control = randomcontrol, measures = acc)

```



```{r}
randomtune$y
```


```{r}
randomtune$x
```
The above are the best Tuning variable

```{r}
randomtree = setHyperPars(randomforest, par.vals = randomtune$x)
randomtrain = train(randomtree, traintask)
getLearnerModel(randomtrain)

```


```{r}
randompredict = predict(randomtrain,testtask)
table(Autotest$high_mileage, randompredict$data$response)
```
here the accuraccy is 92.5%
-----------------------------------------------------------------------------------------------------------------
e. Boosting with tuning
```{r}

library(mlr)
set.seed(1)
boost = makeLearner("classif.gbm", predict.type = "response")

gbmcontrol =  makeTuneControlRandom(maxit = 50L)

gbmcv = makeResampleDesc("CV",iters = 3L)






gbmparam =  makeParamSet(makeDiscreteParam("distribution", values = "bernoulli"),
makeIntegerParam("n.trees", lower = 700, upper = 1000), #number of trees
makeIntegerParam("interaction.depth", lower = 2, upper = 6), #depth of tree
makeIntegerParam("n.minobsinnode", lower = 10, upper = 50),
makeNumericParam("shrinkage",lower = 0.01, upper = 0.7))



gbmtune = tuneParams(learner = boost, task = traintask, par.set = gbmparam, control = gbmcontrol, measures = acc, resampling = gbmcv)
```
```{r}
gbmtune$y
```


```{r}
gbmtune$x
```

```{r}
gbmboost = setHyperPars(boost,par.vals = gbmtune$x)
```
```{r}
gbmtrain = train(gbmboost,traintask)
gbmpredict = predict(gbmtrain,testtask)
table(Autotest$high_mileage,gbmpredict$data$response)
```

Here the Acuuracy is 93.8%
-----------------------------------------------------------------------------------------------------------------
f. SVM with linear kernel tuning



creating an learner , hyperparameter and Grid controller
```{r}
set.seed(1)
svmlearnerl = makeLearner("classif.ksvm", predict.type = "response")

randomcross = makeResampleDesc("CV",iters = 3L)

svmparameter<- makeParamSet(makeNumericParam("C", lower = -5, upper = 5, trafo = function(x) 2^x))


svmcontrol = makeTuneControlGrid()
svmtunel = tuneParams(svmlearnerl, task = traintask, resampling = randomcross, par.set  = svmparameter, control = svmcontrol, measures = acc)
```
```{r}
svmtunel$x
```


```{r}
svmtunel$y
```
```{r}
svmmodell = setHyperPars(svmlearnerl,par.vals = svmtunel$x)
svmtrainl = train(svmmodell, traintask)
getLearnerModel(svmtrainl)

```

```{r}
predictsvml = predict(svmtrainl, testtask)
table (Autotest$high_mileage, predictsvml$data$response)
```
Here the acuuracy is 91%

g. SVM with polynomial kernel and tuning


```{r}
set.seed(1)
svmlearner = makeLearner("classif.ksvm", predict.type = "response")

randomcross = makeResampleDesc("CV",iters = 3L)

svmparameter<- makeParamSet(makeNumericParam("C", lower = -5, upper = 5, trafo = function(x) 2^x),
                            makeDiscreteParam("sigma", values = 2^c(-8,-4,0,4))) #RBF Kernel Parameter

svmcontrol = makeTuneControlGrid()
svmtune= tuneParams("classif.ksvm", task = traintask, resampling = randomcross, par.set  = svmparameter, control = svmcontrol, measures = acc)
```

```{r}
svmtune$y
```



```{r}
svmtune$x

```




```{r}
svmmodel = setHyperPars(svmlearner,par.vals = svmtune$x)
svmtrain = train(svmmodel, traintask)
getLearnerModel(svmtrain)
```


```{r}
predictsvm = predict(svmtrain, testtask)
table (Autotest$high_mileage, predictsvm$data$response)
```
Same here the accuracy is also 89%

-----------------------------------------------------------------------------------------------------------------




-----------------------------------------------------------------------------------------------------------------

h. LDA analysis(bonus 5):
```{r}
ldalearner = makeLearner("classif.lda", predict.type = "response")
ldatrain = train(ldalearner, traintask)
predictlda = predict(ldatrain, testtask)
table(Autotest$high_mileage, predictlda$data$response)
```
Here the LDA accuracy is 91 %


```{r}
cvlda = crossval(ldalearner, task = traintask, iters = 3,stratify = TRUE,measures = acc,show.info = F)
cvlda$aggr
```





-----------------------------------------------------------------------------------------------------------------

5. Report
a. Report the accuracy if you predicted the most frequent class for all observations. This is
your baseline.






-----------------------------------------------------------------------------------------------------------------
b. Plot of cross validation accuracy as a function of the tuning parameter for each classifier.

```{r}
x = c("Logistic reg", "decision tree", "Bagging","ran forest","Bosting","SVM linear","SVM poly","LDA")
y =c(0.8906833,0.9388105 ,0.9164315, 0.8937018,0.9258464 ,0.9226724,0.9130259,0.8778 )
z = c(93,92,93,92.5,93.8,91,89,91) 
names(y) = x
names(z) = x
```


```{r}
graph = as.data.frame(x)
graph$crossvalaccuracy = y
graph$accuracy = z
```
```{r}
plot(graph$x,graph$crossvalaccuracy , xlim= c(1,8),cex.axis = 0.8)

```
```{r}
plot(graph$x,graph$accuracy , xlim= c(1,8),cex.axis = 0.8)
```

-----------------------------------------------------------------------------------------------------------------

i. For the decision tree, plot the tree.


```{r}
library(rattle)	
fancyRpartPlot(destree$learner.model)	
```


-----------------------------------------------------------------------------------------------------------------



c. Which classifier does best?


After the Analysis Bossting with tuning doing better. as we can see the Cv Accuracy graph and accuracy Graph.

-----------------------------------------------------------------------------------------------------------------
d. Which one would you use? And does this classifier match your initial guess?


We boosting or decision as boosting Performance is better.
Decision trees implicitly perform variable screening or feature selectionso will have model which process all the features also for this dataset it performence is considerably better nxt to bossting.









-----------------------------------------------------------------------------------------------------------------
