---
title: "Train of Caret"
author: "Bhasheyam""
date: "3 December 2017"
output: html_document
---
---
title: "Machine Leanrning"
author: "Bhasheyam"
date: "1 November 2017"
output: html_document
---
```{r}

iris

```

Before try to fit a model it is better to study the dataset to find a better fit.

```{r}
cor(subset(iris,select=-Species))
```

From the above
petal width and petal length
Septal.length and petal.length, petal width are well corelated 

```{r}
library(ggvis)
iris %>% ggvis(~Sepal.Length,~Petal.Length, fill = ~Species) %>% layer_points()
```
```{r}
library(ggvis)
iris %>% ggvis(~Petal.Width, ~Petal.Length, fill = ~Species) %>% layer_points()
```
```{r}
library(ggvis)
iris %>% ggvis(~Sepal.Length,~Petal.Width , fill = ~Species) %>% layer_points()
```

From the above we can see a positive correlation between these combinations as we can observe from the Graph.


```{r}
lev=levels(iris$Species)
cor(iris[iris$Species==lev[1],1:4])
```
```{r}
lev=levels(iris$Species)
cor(iris[iris$Species==lev[2],1:4])
```
```{r}
lev=levels(iris$Species)
cor(iris[iris$Species==lev[3],1:4])
```
```{r}
summary(iris)
```
```{r}
calculatenorm=function(x){
  num=x-min(x)
  denom=max(x)-min(x)
  return (num/denom)
}
normalizeset= as.data.frame(lapply(iris[1:4],calculatenorm))
normalizeset
```

After the Datasetis normalised 
```{r}
normdata=cbind.data.frame(normalizeset,iris$Species)
normdata
```










```{r}
set.seed(1234)
gp=runif(150)
iris=iris[ordered(gp),]
index1=sample(2, nrow(iris), replace = TRUE, prob = c(0.67, 0.33))
trainingset=iris[index1==1,1:4]
testset=iris[index1==2,1:4]
traininglabel=iris$Species[index1==1]
testlabel=iris[index1==2,5]
testlabel
```

```{r}
names(trainingset)
```

```{r}
library(caret)
model <- train(Species ~ ., data = iris
                        ,method = "pls"
                        )
```



```{r}
summary(model)
```

